Plots for Latent Hawkes Paper

### 2021-09-25 output_scripts/Cohort_level_analysis.Rmd
tidying

---
title: "Cohort Level Analysis"
author: "Owen G. Ward"
date: '`r Sys.Date()`'
output:
  html_document:
    # toc: true
    # toc_depth: 1
    number_sections: true
    # toc_float: true
    code_folding: hide
---

```{r setup, echo=FALSE, message=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, fig.height = 5, fig.width = 7,
  warning = FALSE, cache = TRUE
)

@@

  corrplot(spear_cor,
           type = "upper",
           tl.col = "black",
           col.lim = c(0,1),
           title = "Spearman Rank Correlation",
           mar = c(0, 0, 1, 0), diag = FALSE)
}
```

@@

Here all events which are classified as inactive by the C-MMHP model
originate from the top ranked animal. As such there is strong
agreement between the win/loss matrix of all events and
those ocurring in active periods, with the 
restriction to only active events
slightly decreasing the 
influence of the top ranked animal.

@@

Examing the correlation matrices of both the median ranks for
each of our cohort models and the Spearman rank correlations,
we see that the C-HP most agrees with the I&SI ranking,
with the C-DCHP and C-MMHP models showing progressively less agreement.

@@

We next plot the inferred posterior rank estimates from 
each of our cohort models and the comparison AggRank model,
where we order the animals by the estimated I&SI ranking.

@@

Similarly, to show how this rank differs from that obtained by the C-MMHP
model, we order the animals by the inferred ranking from that
model.

@@

For each of our three proposed models, we show the parameter
estimates for the non rank parameters, including the in and
out degree estimates for the models which incorporate degree
corrections.

@@

Finally, for each animal in this cohort, we summarise

@@

@@

spear_corr_all %>%
  left_join(cohort_summ, by = "cohort") %>% 
  filter(first == "chp") %>% 
  filter(second %in% c("cdchp", "cmmhp")) %>% 
  pivot_wider(id_cols = cohort, names_from = second, 
              values_from = c(value, act_perc)) %>% 
  select(cohort:act_perc_cdchp) %>% 
  rename(act_perc = act_perc_cdchp) %>% 
  mutate(corr_diff = value_cdchp - value_cmmhp) %>% 
  select(cohort, corr_diff, act_perc) %>% 
  ggplot(aes(corr_diff, act_perc)) +
  geom_point() +
  labs(y = "Percent fights Active", x = "Correlation Differernce",
       subtitle = "Correlation difference between C-HP/C-DCHP and C-HP/C-MMHP")
# then join this with cohort summ and do the plot
```

>>>>

---
title: "Supplement:Network Hawkes Process Models for Exploring Latent Hierarchy in Social Animal Interactions"
author: 
date: '`r Sys.Date()`'
output:
  # html_document:
  #   # toc: true
  #   # toc_depth: 1
  #   number_sections: true
  #   # toc_float: true
  #   code_folding: hide
  pdf_document
---

Here we provide some summary analysis for each of the mice cohorts
used in this paper. We include analyses for each cohort 
separately, along with providing some further overall results.

```{r setup, echo=FALSE, message=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, fig.height = 5, fig.width = 7,
  warning = FALSE, cache = TRUE
)
# knitr::opts_chunk$set(echo = FALSE) ### for pdf output

@@

  corrplot(spear_cor,
           type = "upper",
           tl.col = "black",
           col.lim = c(0,1),
           title = "Spearman Rank Correlation",
           mar = c(0, 0, 1, 0), diag = FALSE)
}

cohort_mae <- function(current_cohort) {
  load("../output/revisions/lapl_check/plot_N_predict_revision.RData")
  temp_plot_df <- predict_day_mae_df_lst[[current_cohort]]
  temp_plot_df$method <- factor(temp_plot_df$method,
    levels = c("mmhp", "dsnl", "m1", "m2", "m3"),
    labels = c("I-MMHP", "DSNL", "C-HP", "C-DCHP", "C-MMHP")
  )
  temp_plot_df$day <- factor(temp_plot_df$day)
  # png(paste(plot_path,"real_predict_N_one_cohort.png",sep=""),
  # width=600,height=300)

  plot_cols_pred <- col_df %>%
    filter(method %in% levels(temp_plot_df$method)) %>%
    arrange(factor(method, levels = c(
      "I-MMHP", "DSNL",
      "C-HP", "C-DCHP", "C-MMHP"
    ))) %>%
    pull(cols)

  p3 <- temp_plot_df %>%
    rowwise() %>%
    # mutate(norm = min(norm,60)) %>%
    # rename(Method = method) %>%
    ggplot(aes(x = method, y = mae, fill = method)) +
    geom_boxplot(alpha = 0.7) +
    scale_fill_manual(values = plot_cols_pred) +
    ggtitle("(a)") +
    theme_bw() +
    theme(
      plot.title = element_text(size = 22, hjust = 0.5, face = "bold"),
      text = element_text(size = 20),
      axis.text.x = element_blank(),
      axis.ticks.x = element_blank(),
      legend.position = "right"
    ) +
    facet_grid(cols = vars(day)) +
    xlab("Prediction horizon (day)") +
    ylab("MAE") +
    ylim(0, 5) + # aren't infinite but >150 and <200
    NULL
  p3 + labs(fill = "Method", title = "Single Cohort",
            subtitle = paste("Cohort", current_cohort, sep = " "))
}

@@

<!-- Here all events which are classified as inactive by the C-MMHP model -->
<!-- originate from the top ranked animal. As such there is strong -->
<!-- agreement between the win/loss matrix of all events and -->
<!-- those ocurring in active periods, with the  -->
<!-- restriction to only active events -->
<!-- slightly decreasing the  -->
<!-- influence of the top ranked animal. -->

@@

<!-- Examining the correlation matrices of both the median ranks for -->
<!-- each of our cohort models and the Spearman rank correlations, -->
<!-- we see that the C-HP most agrees with the I&SI ranking, -->
<!-- with the C-DCHP and C-MMHP models showing progressively less agreement. -->

@@

<!-- We next plot the inferred posterior rank estimates from  -->
<!-- each of our cohort models and the comparison AggRank model, -->
<!-- where we order the animals by the estimated I&SI ranking. -->

@@

<!-- Similarly, to show how this rank differs from that obtained by the C-MMHP -->
<!-- model, we order the animals by the inferred ranking from that -->
<!-- model. -->

@@

<!-- For each of our three proposed models, we show the parameter -->
<!-- estimates for the non rank parameters, including the in and -->
<!-- out degree estimates for the models which incorporate degree -->
<!-- corrections. -->

@@

@@

<!-- ### Cohort MAE -->

<!-- ```{r mae-cohort-1} -->
<!-- cohort_mae(current_cohort) -->
<!-- ``` -->

@@

spear_corr_all %>%
  left_join(cohort_summ, by = "cohort") %>% 
  filter(first == "chp") %>% 
  filter(second %in% c("cdchp", "cmmhp")) %>% 
  pivot_wider(id_cols = cohort, names_from = second, 
              values_from = c(value, act_perc)) %>% 
  select(cohort:act_perc_cdchp) %>% 
  rename(act_perc = act_perc_cdchp) %>% 
  mutate(corr_diff = value_cdchp - value_cmmhp) %>% 
  select(cohort, corr_diff, act_perc) %>% 
  ggplot(aes(corr_diff, act_perc)) +
  geom_point() +
  labs(y = "Percent fights Active", x = "Correlation Difference",
       subtitle = "Correlation difference between C-HP/C-DCHP and C-HP/C-MMHP")
# then join this with cohort summ and do the plot
```

### 2021-09-25 output_scripts/Paper_Plots.Rmd
tidying

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, fig.path = "paper_figure/revision/",
  dev = "png", fig.height = 5, fig.width = 7,
  warning = FALSE, cache = TRUE
)

slides_plots <- FALSE
extra_plots <- FALSE

@@

data_path <- "../output/revisions/lapl_check/"

@@

```{r fig-3a-baseline-rate, fig.width=5, fig.height=5, eval=revision_plots}
current_cohort <- 5
## this looks better
# current_cohort <- 6 # 3 is maybe ok, 6/7 is interesting

@@

# png(paste(plot_path,"/lambda0_",
# cohort_names[current_cohort],".png",sep=''),
#     width=400, height=300)
matrixPlotParameter(latent_social_matrix[
  rev(expert_rank_10[[current_cohort]]),
  expert_rank_10[[current_cohort]]
],
xLabels = expert_rank_10[[current_cohort]],
yLabels = rev(expert_rank_10[[current_cohort]]),
title = "(a)" )
# mtext(text=c(1,2,11,6,7,9), side=1, line=-0.35, outer=TRUE, cex=1.3,
#       at=1/17.8*seq(2,12,2)+0.09)
# dev.off()
```

@@

```{r fig-3b-residual-structure, include=TRUE, fig.width=10, fig.height=5, eval=revision_plots}
### this looks better
### now to add Pearson residual matrices here for C-HP and C-DCHP from fig 7
current_cohort <- 5
data_path <- "../output/revisions/lapl_check/"
## 2 and 8 maybe look better
## 3 probably looks the best

@@

matrix_lst_plot <- list(
  m1_pr[
    rev(expert_rank_10[[current_cohort]]),
    expert_rank_10[[current_cohort]]
  ],
  m2_pr[
    rev(expert_rank_10[[current_cohort]]),
    expert_rank_10[[current_cohort]]
  ]
  # ,
  # m3_pr[
  #   rev(expert_rank_10[[current_cohort]]),
  #   expert_rank_10[[current_cohort]]
  # ]
)
# cat("Cohort ",current_cohort,"\n",sep="")
myMultiMatrixPlot(
  X = matrix_lst_plot, no_matrix = 2, n_row = 1,
  xLabels = expert_rank_10[[current_cohort]],
  yLabels = rev(expert_rank_10[[current_cohort]]),
  min = -80, max = 80, axis_cex = 2, title_cex = 1.8,
  colorPalette = "RdBu", if.emp = FALSE,
  # legend.mar=c(0.5,.5,0.5,0.5),
  title_lst = list("C-HP", "C-DCHP", "C-MMHP"),
  # title_lst = list("I-MMHP"),
  col_axis = c(-80, -40, 0, 40, 80), fake_matrix = TRUE,
  matrix.mar = c(2.5, 2.5, 2.5, 1)
)
mtext(text="(b)",side=3,line=0.5,outer=TRUE,cex=2.5,font=2)

@@

```{r fig-4a, eval = revision_plots, message=FALSE, warning=FALSE}
sim_data_path <- here("output", "revisions", "aug_run", "sims", "/")

@@

```{r prepare data for 4b,cache=TRUE, eval=TRUE}
plot.s <- 26 # 8 is pretty good
plot.i <- 10
plot.j <- 9

@@

```{r fig-4b-recover-latent-states,fig.width=8,fig.height=4, eval=TRUE}
mmhp_lty <- 1

@@

```{r fig-4b, eval=TRUE}
layout(matrix(c(1:6), 6, 1), heights = rep(c(7.5, 2.5), 3))
par(
  mar = c(0.2, 0.3, 0, 0.1), oma = c(3, 3.5, 4, 2),
  tcl = 0.2, mgp = c(0.5, 0, 0), xpd = TRUE
)

@@

```{r data for fig 5,cache=TRUE, eval=revision_plots}
n_sim <- 50
num_nodes <- 10

@@

@@

```{r fig-5b-spearman-sim, fig.height=5}
sim_files <- list.files(here("output",
                             "revisions",
                             "lapl_check",
                             "sim_rank/"), 
                        pattern = "rank_sim")

@@

for (i in seq_along(sim_files)) {
  single_fit <- readRDS(here(
    "output",
    "revisions", 
    "lapl_check",
    "sim_rank",
    sim_files[i]
  ))
  all_sims[[i]] <- single_fit
}

@@

## Figure 6a: Rank vs I&SI

```{r fig-6a-rank-vs-isi}
### Rank Comparison for Single Cohort ####
current_cohort <- 5
# want to update this now
# data_path

@@

## Figure 6b: Spearman rank correlation

```{r fig-6b-overall-rank-correlation}
load("../output/revisions/lapl_check/weighted_rank_data.RData")
# png(paste(plot_path,"real_rank_all_cohort.png",sep=""),width=600,height=300)
no_method <- 4
plot_cor_df <- data.frame(
  Method = rep(c(1:no_method), each = 10),
  cor = as.vector(spearman_df)
)
plot_cor_df$Method <- factor(plot_cor_df$Method,
  labels = c("Agg-rank", "C-HP", "C-DCHP", "C-MMHP")
)
p2 <- ggplot(plot_cor_df, aes(x = "", y = cor, fill = Method)) +
  geom_boxplot(alpha = 0.7, width = 0.5) +
  scale_fill_manual(values = plot_cols) +
  ggtitle("(b)") +
  ylim(0, 1) +
  theme_bw() +
  theme(
    plot.title = element_text(size = 22, hjust = 0.5, face = "bold"),
    text = element_text(size = 20),
    axis.text.y = element_text(size = 11),
    legend.position = "none",
    axis.title.x = element_blank()
  ) +
  facet_grid(cols = vars(Method)) +
  ylab("Spearman rank correlation")
p2
```

@@

```{r fig-7-prMatrix-Cohort3, fig.width=7, fig.height=7}
current_cohort <- 5
data_path <- "../output/revisions/lapl_check/"
## 2 and 8 maybe look better
## 3 probably looks the best

@@

```{r fig-8a-mae-norm-cohort5, fig.width=8,fig.height=4,eval=TRUE}
load("../output/revisions/lapl_check/plot_N_predict_revision.RData")
current_cohort <- 5 # cohort 1 looks worse than rest

@@

```{r fig-7a-pred-all-cohorts-box-mae,eval=TRUE, fig.width=8, fig.height=4}
### updated to revision
load("../output/revisions/lapl_check/plot_N_predict_revision.RData")

@@

```{r fig-9a-spearman-rank-cohort1, eval=FALSE}
load(here("output",
          "revisions",
          "lapl_check",
          "plot_rank_predict.RData"))
# current_cohort <- 5
temp_plot_df <- predict_day_rank_df_lst[[current_cohort]]
temp_plot_df$method <- factor(temp_plot_df$method,
  levels = c("mmhp", "dsnl", "m1", "m2", "m3"),
  labels = c(
    "I-MMHP", "DSNL", "C-HP",
    "C-DCHP", "C-MMHP"
  )
)
temp_plot_df$day <- factor(temp_plot_df$day)
# png(paste(plot_path,"real_predict_rank_one_cohort.png",sep=""),
# width=600,height=300)
p5 <- ggplot(temp_plot_df, aes(x = method, y = spearman, fill = method)) +
  geom_boxplot(alpha = 0.7) +
  scale_fill_manual(values = plot_cols_pred) +
  # scale_fill_manual(values =
  # c("gray","yellowgreen","steelblue","goldenrod2","firebrick2")) +
  ggtitle("(a)") +
  theme_bw() +
  theme(
    plot.title = element_text(size = 22, hjust = 0.5, face = "bold"),
    text = element_text(size = 20),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    legend.position = "right"
  ) +
  facet_grid(cols = vars(day)) +
  xlab("Prediction horizon (day)") +
  ylab("Spearman rank correlation") +
  # ylim(0, 1) +
  NULL
p5 + labs(fill = "Method")
```

@@

```{r fig-7b-pred-rank-spearman-all-cohorts}
load("../output/revisions/lapl_check/plot_rank_predict.RData")

@@

p7 <- ggplot(
  all_cohort_rank_df,
  aes(x = method, y = spearman, fill = method)
) +
  # geom_line(size=1.2, alpha=0.8, position=position_dodge(0.2)) +
  geom_boxplot(alpha = 0.7) +
  scale_fill_manual(values = plot_cols_pred) +
  ggtitle("(b)") +
  theme_bw() +
  theme(
    plot.title = element_text(size = 22, hjust = 0.5, face = "bold"),
    text = element_text(size = 20),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    legend.position = "right"
  ) +
  facet_grid(cols = vars(day)) +
  xlab("Prediction horizon (day)") +
  ylab("Spearman rank corr.") +
  # coord_cartesian(ylim=c(0,1)) +
  labs(fill = "Method")

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, fig.path = "paper_figure/revision/",
  dev = "png", fig.height = 5, fig.width = 7,
  warning = FALSE, cache = FALSE
)

slides_plots <- FALSE
extra_plots <- FALSE
fig4 <- FALSE

@@

@@

```{r fig-3a-baseline-rate, fig.width=5, fig.height=5}
current_cohort <- 5
## this looks better
# current_cohort <- 6 # 3 is maybe ok, 6/7 is interesting

@@

# png(paste(plot_path,"/lambda0_",
# cohort_names[current_cohort],".png",sep=''),
#     width=400, height=300)
matrixPlotParameter(latent_social_matrix[
  rev(expert_rank_10[[current_cohort]]),
  expert_rank_10[[current_cohort]]
],
xLabels = expert_rank_10[[current_cohort]],
yLabels = rev(expert_rank_10[[current_cohort]]))
mtext(text="(a)",
      side = 3,
      line = 0.5,
      outer = TRUE,
      cex = 2.5,
      font = 2)
# mtext(text=c(1,2,11,6,7,9), side=1, line=-0.35, outer=TRUE, cex=1.3,
#       at=1/17.8*seq(2,12,2)+0.09)
# dev.off()
```

@@

```{r fig-3b-residual-structure, include=TRUE, fig.width=10, fig.height=5, eval=revision_plots}
### this looks better
### now to add Pearson residual matrices here for C-HP and C-DCHP from fig 7
current_cohort <- 5
## 2 and 8 maybe look better
## 3 probably looks the best

@@

matrix_lst_plot <- list(
  m1_pr[
    rev(expert_rank_10[[current_cohort]]),
    expert_rank_10[[current_cohort]]
  ],
  m2_pr[
    rev(expert_rank_10[[current_cohort]]),
    expert_rank_10[[current_cohort]]
  ]
  # ,
  # m3_pr[
  #   rev(expert_rank_10[[current_cohort]]),
  #   expert_rank_10[[current_cohort]]
  # ]
)
# cat("Cohort ",current_cohort,"\n",sep="")
myMultiMatrixPlot(
  X = matrix_lst_plot, no_matrix = 2, n_row = 1,
  xLabels = expert_rank_10[[current_cohort]],
  yLabels = rev(expert_rank_10[[current_cohort]]),
  min = -90, max = 90, axis_cex = 1.6, title_cex = 1.8,
  colorPalette = "RdBu", if.emp = FALSE,
  # legend.mar=c(0.5,.5,0.5,0.5),
  title_lst = list("C-HP", "C-DCHP", "C-MMHP"),
  # title_lst = list("I-MMHP"),
  col_axis = c(-90, -45, 0, 45, 90), fake_matrix = TRUE,
  matrix.mar = c(2.5, 2.5, 2.5, 1)
)
mtext(text="(b)",side=3,line=0.5,outer=TRUE,cex=2.5,font=2)

@@

```{r fig-4a, eval = fig4, message=FALSE, warning=FALSE}
sim_data_path <- here("output", "revisions", "aug_run", "sims", "/")

@@

```{r prepare data for 4b,cache=TRUE, eval=fig4}
plot.s <- 26 # 8 is pretty good
plot.i <- 10
plot.j <- 9

@@

```{r fig-4b-recover-latent-states,fig.width=8,fig.height=4, eval=fig4}
mmhp_lty <- 1

@@

```{r fig-4b, eval=fig4}
layout(matrix(c(1:6), 6, 1), heights = rep(c(7.5, 2.5), 3))
par(
  mar = c(0.2, 0.3, 0, 0.1), oma = c(3, 3.5, 4, 2),
  tcl = 0.2, mgp = c(0.5, 0, 0), xpd = TRUE
)

@@

```{r data for fig 5,cache=TRUE, eval=FALSE}
n_sim <- 50
num_nodes <- 10

@@

sim_data_path <- here("output", "revisions", "aug_run", "sims", "/")

@@

```{r fig-5b-spearman-sim, fig.height=5}
sim_files <- list.files(here("output",
                             "revisions",
                             "aug_run",
                             "sim_rank/"), 
                        pattern = "rank_sim")

@@

for (i in seq_along(sim_files)) {
  single_fit <- readRDS(here(
    "output",
    "revisions", 
    "aug_run",
    "sim_rank",
    sim_files[i]
  ))
  all_sims[[i]] <- single_fit
}

@@

## Figure 6a: Rank vs I&SI Cohort 5

```{r fig-6a-rank-vs-isi-cohort5}
### Rank Comparison for Single Cohort ####
current_cohort <- 5
# want to update this now
# data_path

@@

## Figure 6b: Rank vs I&SI Cohort 3

```{r fig-6b-rank-vs-isi-cohort3}
### Rank Comparison for Single Cohort ####
current_cohort <- 3
# want to update this now
# data_path

p1 <- ggplot(plot_latent_df, aes(x = Mice, y = force, fill = Method)) +
  geom_boxplot(alpha = 0.7) +
  scale_fill_manual(values = plot_cols) +
  ggtitle("(a)") +
  theme_bw() +
  theme(
    plot.title = element_text(size = 22, hjust = 0.5, face = "bold"),
    text = element_text(size = 20),
    axis.text.x = element_text(size = 10),
    legend.position = "none"
  ) +
  facet_grid(cols = vars(Method)) +
  xlab("Mice (ranked by I&SI method)") +
  ylab("Latent rank")
p1
# dev.off()
current_cohort <- 5
```

```{r fig-6b-overall-rank-correlation, eval=FALSE}
load("../output/revisions/aug_run/weighted_rank_data.RData")
# png(paste(plot_path,"real_rank_all_cohort.png",sep=""),width=600,height=300)
no_method <- 4
plot_cor_df <- data.frame(
  Method = rep(c(1:no_method), each = 10),
  cor = as.vector(spearman_df)
)
plot_cor_df$Method <- factor(plot_cor_df$Method,
  labels = c("Agg-rank", "C-HP", "C-DCHP", "C-MMHP")
)
p2 <- ggplot(plot_cor_df, aes(x = "", y = cor, fill = Method)) +
  geom_boxplot(alpha = 0.7, width = 0.5) +
  scale_fill_manual(values = plot_cols) +
  ggtitle("(b)") +
  ylim(0, 1) +
  theme_bw() +
  theme(
    plot.title = element_text(size = 22, hjust = 0.5, face = "bold"),
    text = element_text(size = 20),
    axis.text.y = element_text(size = 11),
    legend.position = "none",
    axis.title.x = element_blank()
  ) +
  facet_grid(cols = vars(Method)) +
  ylab("Spearman rank correlation")
p2
```

@@

```{r fig-7-prMatrix-Cohort3, fig.width=7, fig.height=7}
current_cohort <- 5
## 2 and 8 maybe look better
## 3 probably looks the best

@@

```{r fig-8a-mae-norm-cohort5,eval=TRUE}
load("../output/revisions/aug_run/plot_N_predict_revision.RData")
current_cohort <- 5 # cohort 1 looks worse than rest

@@

```{r fig-7a-pred-all-cohorts-box-mae,eval=TRUE}
### updated to revision
load("../output/revisions/aug_run/plot_N_predict_revision.RData")

@@

```{r fig-9a-spearman-rank-cohort1, eval=FALSE}
load(here("output",
          "revisions",
          "aug_run",
          "plot_rank_predict.RData"))
# current_cohort <- 5
temp_plot_df <- predict_day_rank_df_lst[[current_cohort]]
temp_plot_df$method <- factor(temp_plot_df$method,
  levels = c("mmhp", "dsnl", "m1", "m2", "m3"),
  labels = c(
    "I-MMHP", "DSNL", "C-HP",
    "C-DCHP", "C-MMHP"
  )
)
temp_plot_df$day <- factor(temp_plot_df$day)
# png(paste(plot_path,"real_predict_rank_one_cohort.png",sep=""),
# width=600,height=300)
p5 <- ggplot(temp_plot_df, aes(x = method, y = spearman, fill = method)) +
  geom_boxplot(alpha = 0.7) +
  scale_fill_manual(values = plot_cols_pred) +
  # scale_fill_manual(values =
  # c("gray","yellowgreen","steelblue","goldenrod2","firebrick2")) +
  ggtitle("(a)") +
  theme_bw() +
  theme(
    plot.title = element_text(size = 22, hjust = 0.5, face = "bold"),
    text = element_text(size = 20),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    legend.position = "right"
  ) +
  facet_grid(cols = vars(day)) +
  xlab("Prediction horizon (day)") +
  ylab("Spearman rank correlation") +
  # ylim(0, 1) +
  NULL
p5 + labs(fill = "Method")
```

@@

```{r fig-7b-pred-rank-spearman-all-cohorts}
load("../output/revisions/aug_run/plot_rank_predict.RData")

@@

p7 <- ggplot(
  all_cohort_rank_df,
  aes(x = method, y = spearman,
      fill = method)) +
  # geom_line(size=1.2, alpha=0.8, position=position_dodge(0.2)) +
  geom_boxplot(alpha = 0.7) +
  scale_fill_manual(values = plot_cols_pred) +
  ggtitle("(b)") +
  theme_bw() +
  theme(
    plot.title = element_text(size = 22, hjust = 0.5, face = "bold"),
    text = element_text(size = 20),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    legend.position = "right"
  ) +
  facet_grid(cols = vars(day)) +
  xlab("Prediction horizon (day)") +
  ylab("Spearman rank corr.") +
  # coord_cartesian(ylim=c(0,1)) +
  labs(fill = "Method")
